\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in, top=0.6in, right=0.75in, bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{ifsym}
\usepackage{fancyhdr}
\usepackage{xcolor} % Add this line

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE DEV SANGHANI}} & Email : \href{mailto:dvsangha@mtu.edu}{dvsangha@mtu.edu}\\
  \href{https://www.linkedin.com/in/devanshusanghani/}{linkedin.com/in/devanshusanghani} & Mobile : +1 (906)-299-2984 \\
  Chicago, IL (Open to relocate) & \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Associate}{Sep. 2022 -- Present}
      {Michigan Technological University}{Houghton, MI}
      \resumeItemListStart
      \resumeItem{Cybersecurity Training}
          {Managed and instructed over 40 students in cybersecurity best practices for various Graduate and Undergraduate-level classes, emphasizing defense mechanisms and secure system architectures.}
        \resumeItem{Infrastructure Management}
          {Built and managed a Dell R640 server equipped with 3 T4 GPUs and 780GBs of RAM, designed for advanced AI computing. Implemented robust cybersecurity practices and security rules to safeguard the server from potential threats.}
          \resumeItem{Virtual Teaching Assistant}
          {Spearheaded an end-to-end virtual teaching assistant project used by over 30 students for their courses.}
          \resumeItem{Virtual Teaching Assistant Architecture}
        {
          Utilized a Retrieval-Augmented Generation (RAG) architecture to manage local knowledge for LLMs. Experimented with models like Mistral, OpenAI’s GPT-3, GPT-4, and Llama 2, integrating BAAI/bge-small-en for embedding generation. Employed OpenAI’s APIs for extended functionality. Containerized the web application using Docker, developing the frontend with Python-based FastAPI and Gradio.
        }
        
      \resumeItemListEnd

    \resumeSubheading
      {Information Security Intern}{June 2023 -- Dec 2023}
      {AirBoss of America Corp.}{Houghton, MI}      
      \resumeItemListStart
        \resumeItem{Data Classification Project}
          {Led a large-scale data classification project for categorizing diverse data types using Azure's compliance hub and Azure Purview.}
        \resumeItem{Data Loss Prevention Policies}
          {Developed detailed Data Loss Prevention Policies (DLP) aligning with NIST 800-171 standards, enhancing data compliance by 40\%.}
        \resumeItem{Incident Response}
          {Played a key role in the rapid response team for email-based threats, enhancing organizational resilience against phishing and malware. Specialized in threat remediation by removing malware and addressing account/machine compromises, thus successfully mitigating security threats.}
          \resumeItem{Vulnerability Assessments and Remediation}
          {Conducted comprehensive security assessments, identifying vulnerabilities and enhancing defenses, particularly in cloud environments.}
          \resumeItem{Security Solutions Engineering}
          {Architected and implemented a Double Key Encryption (DKE) solution using .NET, enhancing data protection. Configured Azure WAF Firewall and geolocation blocking to fortify cloud environments, aligning with NIST 800-171 compliance requirements.}
        \resumeItem{User Sessions and Surveys}
          {Conducted impactful user sessions and surveys for 500+ company employees, leading to a 20\% improvement in overall company data security posture.}
      \resumeItemListEnd

  \resumeSubheading
    {Senior (Software) Systems Engineer}{Oct 2020 -- Jul 2022}
    {Infosys Ltd.}{Bangalore, India}
    \resumeItemListStart
      \resumeItem{Web Apps Revamp}
        {Revamped legacy windows apps into Angular-based web apps, while developing a .NET REST API.}
      \resumeItem{Production Optimization}
        {Optimized production environment by slashing downtime, improving SQL queries and boosting performance by 20\%.}
      \resumeItem{Documentation}
        {Produced comprehensive documentation for onboarding, ticketing, recurring bugs and their fixes, lifting efficiency of SLA deliverables by 35\%.}
      \resumeItem{Team Mentorship}
        {Mentored a 5-member team, clarifying project architecture and CI/CD pipelines.}
      \resumeItem{Technology Stack}
        {Utilized Angular for frontend, .NET for backend, SQL Server for database management, TFS for version control, and Azure VMs for hosting.}
      \resumeItem{Agile Methodology}
        {Followed agile methodology for project management and used Azure Boards for streamlining workflow.}
      \resumeItem{Awards and Recognition}
        {
          \begin{itemize}
            \item Received \textit{INSTA Award} for review effectiveness, improved quality of deliverables by 20\% and extending and aligning with the team's need.
          \end{itemize}
        }
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Technical Skills}
      {Azure, Linux, Agile, Scrum, Docker, Automation, Git, OOPs, TFS, Angular, RAG, LLMs, Rest-APIs, Huggingface}
    \resumeSubItem{Security Skills}
      {Cloud Security, Vulnerability Assessment, Cybersecurity Administration, Security Integration, Security Operations, Email Security, Azure Compliance, Microsoft Defender 365, Triage, NIST, Incident Response, Microsoft Entra ID, Wireshark, Hashcat, Cryptography, Open-Source Intelligence, Security Auditing}
    \resumeSubItem{Programming}
      {Python, C++, Typescript, SQL}
    \resumeSubItem{Communicative Languages}
      {Native Proficiency - English, Gujarati, Hindi}
    \resumeSubItem{Certificates}
      {Python by Coursera, National Cyber League 2023 (CTF), CompTIA Security+ (preparing)}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Michigan Technological University}{Houghton, MI}
      {Master of Science in Cybersecurity; GPA: 3.95}{Aug. 2022 -- April 2024}
    \resumeSubheading
      {SRM Institute of Science and Technology}{Chennai, India}
      {Bachelor of Technology in Software Engineering; GPA: 3.5}{June 2016 -- May 2020}
  \resumeSubHeadingListEnd
  
%-----------PROJECTS AND EVENTS-----------------
\section{Events}
  \resumeSubHeadingListStart
  \resumeSubItem{Red Team - CyberSecurity Student Organization \& Networking and Computing Student Association, Michigan Tech}
      {Current/Last Competitions and conferences - eCTF by Mitre, CyberSeed(12/196), National Cyber League (NCL)(17/365), CypherCon, and SecretCon.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
